Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-21 paper/main.tex
paper

In this work, we propose and analyze uMM, an EDA specifically designed for
black-box combinatorial optimization under a limited budget. The proposed uMM \ldots\MANUEL{what is the inspiration}
\

>>>>

In this work, we propose and analyze uMM, an EDA specifically designed for
black-box combinatorial optimization under a limited budget. The proposed uMM 
\EKHINE{yo no diria que es un EDA porque  no hay generaciones de muestras que compiten }
\ldots\MANUEL{what is the inspiration}
\EKHINE{we propose a probabilistic algrithm that (like cego?) (1) iteratively adds solutions to the sample and (2) fits a surrogate model for every new sample obtained. However,  different fom cego, our surrogate model is an estimation of the predicted fitness function at each point. CEGO controls the  intensification-explotation balance with the expected improvement??? We mimic the intensification-explotation balance by automatically controllong the variance of our surrogate model.}
